---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(scholar)
require(magrittr)
require(dplyr)
library(DT)
```

## **Analysis Support and Consulting**

The bioinformatics team provides analysis support for all biological data. The team has a large pool of experience in analysis support from initial data processing and QC through to publication.

As a team, we have analysed more than 10000 high throughput sequencing datasets (including ATAC-seq, ChIP-seq, ChIP-exo, bulk and single cell RNA-seq, MNase-seq, sgRNA-seq and whole genome resequencing) and have contributed to peer-reviews publications and software from The Rockefeller University.
<br/><br/>

## **Examples of analysis projects**

- Single cell RNA-seq analysis of changes in gene expression and identification of cell specific pathways.Mapping of transcription factor targets from ChIP-seq and correlation of targets with expression from associated Knock Out experiments.
- Evaluation of genes important to survival after treatment using sgRNA-seq.
- Identification of transcript selection, differential exon usage and splicing motifs in RNA-seq data.
- Analysis and visualization of evolutionary conserved motifs around functional elements.

If you have a question about present or future analysis or require analysis support please contact Thomas Carroll (brc@rockefeller.edu).
<br/><br/>

## **Full list of authorships for BRC members**

```{r,echo=FALSE, warning=FALSE, message=FALSE}

scholarIDs <- c("W_54zuEAAAAJ&hl","M4z_6poAAAAJ","H5XCHi0AAAAJ",
                "4wmnEI4AAAAJ","nnaXNlgAAAAJ")
pubCache <- "publications.csv"

tidyPubs <- function(x){
  x %>%
    distinct %>%
    select(title,author,journal,year) %>%
    distinct %>%
    arrange(desc(year))
}

# Google Scholar has no API and blocks datacenter IPs, so get_publications()
# often returns a bare NA when run from CI. Keep only the real data frames.
fetched <- lapply(scholarIDs, function(id){
  # scholar warns once per failed retry before it gives up and returns NA
  res <- suppressWarnings(tryCatch(get_publications(id), error = function(e) NULL))
  if (is.data.frame(res) && nrow(res) > 0) res else NULL
})
fetched <- Filter(Negate(is.null), fetched)

if (length(fetched) == length(scholarIDs)) {
  # Every profile answered, so this is a complete list - refresh the cache.
  allPubs <- tidyPubs(do.call(rbind, fetched))
  write.csv(allPubs, pubCache, row.names = FALSE)
} else if (file.exists(pubCache)) {
  # Partial or empty fetch. A partial list would drop whole authors, so prefer
  # the last complete one and leave the cache untouched.
  allPubs <- read.csv(pubCache, stringsAsFactors = FALSE)
} else if (length(fetched) > 0) {
  allPubs <- tidyPubs(do.call(rbind, fetched))
} else {
  allPubs <- NULL
}

if (is.null(allPubs)) {
  knitr::asis_output("*The publication list is temporarily unavailable.*")
} else {
  datatable(allPubs, rownames = FALSE)
}
```
